Introduction to Markov state modeling with the PyEMMA software --- v\versionnumber

### 2018-09-18 manuscript/manuscript.tex
fixing section reference

In order to interpret the slowest relaxation timescales, we refer to the (right) eigenvectors,
as they are independent of the stationary distribution (see Section~\ref{sec:theory)}.
This enables us to specifically study what conformational changes are happening on a particular timescale independently of the equilbrium distribution.
The first right eigenvector corresponds to the stationary process and its eigenvalue is the Perron eigenvalue~$1$.
The second right eigenvector, on the other hand, corresponds to the slowest process in the system. 
Note that the eigenvectors are real as detailed balance has been enforced during MSM estimation.
The minimal and maximal components of the second right eigenvector indicate the microstates between which the process shifts probability density.
The relaxation timescale of this exchange process is exactly the corresponding implied timescale,
which can be computed from its corresponding eigenvalue using~\eqref{eq:its}.
In the projection onto the first two TICA components,
we identify the slowest MSM process as a probability shift between macrostate $\mathcal{S}_1$ and the rest of the system,
with macrostates $\mathcal{S}_4$ and $\mathcal{S}_5$ in particular (Fig.~\ref{fig:msm-analysis}c).

>>>>

In order to interpret the slowest relaxation timescales, we refer to the (right) eigenvectors,
as they are independent of the stationary distribution (see Section~\ref{sec:theory}).
This enables us to specifically study what conformational changes are happening on a particular timescale independently of the equilbrium distribution.
The first right eigenvector corresponds to the stationary process and its eigenvalue is the Perron eigenvalue~$1$.
The second right eigenvector, on the other hand, corresponds to the slowest process in the system. 
Note that the eigenvectors are real as detailed balance has been enforced during MSM estimation.
The minimal and maximal components of the second right eigenvector indicate the microstates between which the process shifts probability density.
The relaxation timescale of this exchange process is exactly the corresponding implied timescale,
which can be computed from its corresponding eigenvalue using~\eqref{eq:its}.
In the projection onto the first two TICA components,
we identify the slowest MSM process as a probability shift between macrostate $\mathcal{S}_1$ and the rest of the system,
with macrostates $\mathcal{S}_4$ and $\mathcal{S}_5$ in particular (Fig.~\ref{fig:msm-analysis}c).
